Software Citation Principles

### 2016-07-25 sc-principles/rebuttal/rebuttal.tex

\textbf{Our response:}
We view the principles presented at the beginning as the main outcomes\slash results of this work, with the process of producing them (discussed in the new Section 3) based on a synthesis of information from the use cases and related work. Then, Section 6 (previously 5) discusses the ``results''.
Our modifications to the structure of the paper, and changes we hope improve the logical flow, should help indicate these connections better.

\item \textbf{Reviewer comment:}
\emph{It is not clear whether the authors consider software citations to be just the first step towards a long-term vision, or whether they consider software citations the overall final solution. It seems that the first is the case, but the long-term vision is not discussed.}

\textbf{Our response:}
\asnote{Perhaps we should be adding a short paragraph outlining how we believe that ultimately academic publishing should be moving towards sharing all of the products of researcher activity. This work is primarily about making software a citable entity which is just one part of a much larger change in the scholarly ecosystem.}

\niemnote{Dan, can you do this?} \katznote{I was hoping Arfon might do this one}
\niemnote{I think we have something along these lines now at the end of section 3, although perhaps could say more.}

### 2016-07-25 sc-principles/software-citation-principles.tex
slight ack update
adding comments to some use cases, filling out description and steps for B.3

Work by Daniel S.~Katz was supported by the National Science Foundation (NSF) while working at the Foundation.
Any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.
Work by Kyle E.~Niemeyer was supported in part by the NSF under grant ACI-1535065.

@@

maybe a variant of above\niemnote{add more to this?}

@@

\niemnote{this seems the same as use case 1} \katznote{I thought it was the same as 6}
\niemnote{6 is about reproducing, while this seems to be writing a software paper}
The research wants to publish about a version of software they have produced.
A key part of this use case is to be able to connect the given narrative to a specific version of the software in questions and connect that in large story.

@@

\niemnote{Is this distinct from 6? Or should it be a new one?}
This is the case where a researcher is using some software to perform an analysis, either of a physical sample or of data.
The researcher needs to know which version was used, for example in case a bug was fixed.
Note that knowing the software and its version is not sufficient to determine the ``conditions'' of the analysis, but they are essential.

>>>>

Work by Daniel S.~Katz was supported in part by the National Science Foundation (NSF) while working at the Foundation.
Any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.
Work by Kyle E.~Niemeyer was supported in part by the NSF under grant ACI-1535065.

@@

A researcher wants to contribute to someone else's software in the manner in which their contributions will be accepted and recognized.

Possible steps:
\begin{enumerate}
\item Researcher finds information about the software, and how contributors will be recognized
\item Researcher possibly submit a Contributor License Agreement (CLA) or Copyright Assignment Agreement (CAA) to allow the contributed content to be distributed with the software being contributed to
\item Researcher contributes to the software
\item Software maintainers accept contribution, recognize researcher's contribution, and update the software metadata as appropriate
\end{enumerate}

@@

\niemnote{this seems the same as use case 1} \katznote{I thought it was the same as 6}
\niemnote{6 is about reproducing, while this seems to be writing a software paper} \katznote{ok, I guess this is like 1, but in 1, the research is using someone else's software, and here, the researcher is using their own software.  Maybe this doesn't matter so much.  So should we just add a comment that this is the same as 1 other than the fact that the software developer and paper author are mostly the same here?}
The research wants to publish about a version of software they have produced.
A key part of this use case is to be able to connect the given narrative to a specific version of the software in questions and connect that in large story.

@@

\niemnote{Is this distinct from 6? Or should it be a new one?} \katznote{I think this is the same as 1, other than in 1 the research output is a paper, while here, the output is a dataset.}
This is the case where a researcher is using some software to perform an analysis, either of a physical sample or of data.
The researcher needs to know which version was used, for example in case a bug was fixed.
Note that knowing the software and its version is not sufficient to determine the ``conditions'' of the analysis, but they are essential.
